A systematic search for transiting planets in the \KT\ data

### 2015-02-16 ms.tex
MS changes, added Armstrong2014 to bib

Previous projects have developed methods to work with \KT\ data.
\citet{Vanderburg:2014} extract aperture photometry from the pixel data
and decorrelate with image centroid position, producing light curves for each
star that are ``corrected'' for the spacecraft motion.
These data have produced the first confirmed planet found with
\KT\ \citep{Vanderburg:2015}.
Both \citet{Aigrain:2015} and \citet{Crossfield:2015} use a Gaussian Process
model for the measured flux, with pointing measurements as the inputs, and
then ``de-trend'' using the mean prediction from that model.
Other data-driven approaches have been developed and applied to the \kepler\
data \citep[for example,][]{pdc1, pdc2, arc, dun} but they have yet to be
generalized to \KT.

@@

This project follows in the tradition of independently implemented transit
search algorithms applied publicly available datasets \citep[such
as][]{petigura1, petigura2, roberto, dressing}.
These efforts have been hugely successful especially in the field of exoplanet
population inference because, thanks to their relative simplicity, the
efficiency and behavior of these pipelines can be quantified empirically.
The work described in this \paper\ is built on many of the same principles as
the previous projects built for studying \kepler\ data but our main
intellectual contribution is a computationally tractable framework for
simultaneously fitting for the trends and the transit signal even when
searching for planets.

@@

Physically, the motivation for our model---and the \pdc\ model---is that every
star on the detector should be affected by the same set of systematic effects.
These are caused by things like pointing jitter, temperature variations, and
other sources of PSF modulation.
Each of these effects will be imprinted in the light
curves of many stars with varying amplitudes and signs as a result of the
varying flat field and PSF.
Therefore, while it is hard to write down a physical generative model for the
systematics, building a data-driven model might be possible.
This intuition is also exploited by other methods that model the systematics
using only empirical centroids \citep{Vanderburg:2014, Aigrain:2015,
Crossfield:2015}, but our more flexible model should capture a wider range of
effects, including those related to PSF and temperature.
For example, \Fig{corr} shows the application of our model---with 150
ELCs---to a light curve with no known transit signals and the precision is
excellent.
If, however, we were to apply this systematics model alone (without a simultaneous fit
of the exoplanet transit model) to a light curve with
transits, we would be at risk of over-fitting and decreasing the amplitude of
the signal.

@@

The periodic search procedure returned three signals per target so this gave
an initial list of 65,109 candidates.
The vast majority of these signals are not induced by a transiting planet;
there are many false positives.
Therefore to reduce the search space, we estimate the signal-to-noise of each
candidate by comparing the peak height to a robust estimate of variance in
\TIC\ values across period.
This is not the same criterion used to select the initial three peaks but we
find that it produces a more complete and pure sample.
A cut in this quantity can reject most variable stars and low signal-to-noise
candidates that can't be reliably recovered from the data.
Figure~\dfmtodo{SOMEFIGURE} shows the distribution of signal-to-noise for a set of
injections and compares it to the distribution of false candidates that are
proposed by the pipeline.
To minimize contamination from false alarms but maximize our sensitivity, we
choose a threshold of 15.
We also find that the signals with periods $\lesssim 4$ days are strongly
contaminated by false alarms.
This might be because of the fact that our independence assumption
(\eqalt{indtran}) breaks down at these short periods.
Therefore, we discard all signals with periods shorter than 4 days.
After these cuts, we're left with 741 candidates that we then examine by hand.
The full list of peaks and their relevant meta data is available online at
\dfmtodo{SOMEURL}.

@@

This vetting resulted in a list of 101 candidate transit signals.
Many of these signals are due to astrophysical ``false positives'' like
eclipsing binaries or blending.
We address this effect in the following \sectionname, where we separate the list of
candidates into a list of astrophysical false positives and planet candidates.

@@

A major problem with any transit search is the potential confusion between
transiting planets and eclipsing binaries.
Ground-based surveys prior to \kepler\ often had a false-positive rate
of 30 to 40~percent. \dfmtodo{(because of shit?)}
In the primary \kepler\ Mission, this number was significantly lower:
the false positive rate was only 5 to 10~percent \citep{Morton:2011}.
Such improvement was enabled by the relatively small pixels, stable
pointing, and high precision of the \kepler\ spacecraft.
In \kepler\ data, false positives can be reliably separated from
planet candidates by looking for differences in the position of the
centroid of light during transit events with respect to the
out-of-transit data \dfmtodo{(e.g. citation)}, variations in the depth of
alternating transits \dfmtodo{(e.g. citation)}, and evidence for ellipsoidal
variations between transits \dfmtodo{(e.g. citation)}.

In \KT, the precision of these tests is lower and they must be applied with
care.
There are typically only a handful of transits, meaning differences between
``odd'' and ``even'' transits must be large to create a significant
difference.
Searching for ellipsoidal variations is hindered by the short time baseline
and the increased photometric uncertainty in \KT\ data.
Centroid variations are feasible in \KT\ but must be treated differently than
in the original \kepler\ mission where this effect was generally measured
using difference imaging (cite).

@@

In \papertwo, we will characterize the stars for each of our candidates in
detail but for now it's worth noting that about half \dfmtodo{(IS THIS TRUE?)} of our
planet candidates are orbiting M-type stars.
If this rate remains robust after stellar characterization and if these
numbers are representative of the yields in upcoming \KT\ Campaigns, the
\KT\ Mission
will substantially increase the number of planets known to transit cool stars!

>>>>

Previous projects have developed methods to work with \KT\ data.
Both \citet{Vanderburg:2014} and \citet{Armstrong:2014}
extract aperture photometry from the pixel data
and decorrelate with image centroid position, producing light curves for each
star that are ``corrected'' for the spacecraft motion.
These data have produced the first confirmed planet found with
\KT\ \citep{Vanderburg:2015}.
Both \citet{Aigrain:2015} and \citet{Crossfield:2015} use a Gaussian Process
model for the measured flux, with pointing measurements as the inputs, and
then ``de-trend'' using the mean prediction from that model.
Other data-driven approaches have been developed and applied to the \kepler\
data \citep[for example,][]{pdc1, pdc2, arc, dun} but they have yet to be
generalized to \KT.

@@

This project follows in the tradition of independently implemented transit
search algorithms applied to publicly available datasets \citep[such
as][]{petigura1, petigura2, roberto, dressing}.
These efforts have been hugely successful especially in the field of exoplanet
population inference because, thanks to their relative simplicity, the
efficiency and behavior of these pipelines can be quantified empirically.
The work described in this \paper\ is built on many of the same principles as
the previous projects built for studying \kepler\ data but our main
intellectual contribution is a computationally tractable framework for
simultaneously fitting for the trends and the transit signal even when
searching for planets.

@@

Physically, the motivation for our model---and the \pdc\ model---is that every
star on the detector should be affected by the same set of systematic effects.
These are caused by things like pointing jitter, temperature variations, and
other sources of PSF modulation.
Each of these effects will be imprinted in the light
curves of many stars with varying amplitudes and signs as a result of the
varying flat field and PSF.
Therefore, while it is hard to write down a physical generative model for the
systematics, building a data-driven model might be possible.
This intuition is also exploited by other methods that model the systematics
using only empirical centroids \citep{Vanderburg:2014, Armstrong:2014,
Aigrain:2015,
Crossfield:2015}, but our more flexible model should capture a wider range of
effects, including those related to PSF and temperature.
For example, \Fig{corr} shows the application of our model---with 150
ELCs---to a light curve with no known transit signals and the precision is
excellent.
If, however, we were to apply this systematics model alone (without a simultaneous fit
of the exoplanet transit model) to a light curve with
transits, we would be at risk of over-fitting and decreasing the amplitude of
the signal.

@@

The periodic search procedure returned three signals per target so this gave
an initial list of 65,109 candidates.
The vast majority of these signals are not induced by a transiting planet;
there are many false positives.
Therefore to reduce the search space, we estimate the signal-to-noise of each
candidate by comparing the peak height to a robust estimate of variance in
\TIC\ values across period.
This is not the same criterion used to select the initial three peaks but we
find that it produces a more complete and pure sample.
A cut in this quantity can reject most variable stars and low signal-to-noise
candidates that can't be reliably recovered from the data.
Figure~\dfmtodo{SOMEFIGURE} shows the distribution of signal-to-noise for a set of
injections and compares it to the distribution of false candidates that are
proposed by the pipeline.
To minimize contamination from false alarms but maximize our sensitivity, we
choose a threshold of 15.
We also find that the signals with periods $\lesssim 4$ days are strongly
contaminated by false alarms.
This might be because of the fact that our independence assumption
(\eqalt{indtran}) breaks down at these short periods.
Therefore, we discard all signals with periods shorter than 4 days.
After these cuts, 741 candidates remain; we examine these signals by hand.
The full list of peaks and their relevant meta data is available online at
\dfmtodo{SOMEURL}.

@@

This vetting resulted in a list of 101 candidate transit signals.
Many of these signals are due to astrophysical ``false positives'' such as 
eclipsing binary systems, either as the target star or as a background ``blend.''
We address this effect in the following \sectionname, where we separate the list of
candidates into a list of astrophysical false positives and planet candidates.

@@

A major problem with any transit search is the potential confusion between
transiting planets and eclipsing binaries.
Ground-based surveys prior to \kepler\ often had a false-positive rate
of 30 to 40~percent. \dfmtodo{(because of shit?) Because of giant pixels.
See references in Morton and Johnson intro, probably}
In the primary \kepler\ Mission, this number was significantly lower:
the false positive rate was only 5 to 10~percent \citep{Morton:2011}.
Such improvement was enabled by the relatively small pixels, stable
pointing, and high precision of the \kepler\ spacecraft.
In \kepler\ data, false positives can be reliably separated from
planet candidates by looking for differences in the position of the
centroid of light during transit events with respect to the
out-of-transit data \dfmtodo{(e.g. citation)}, variations in the depth of
alternating transits \dfmtodo{(e.g. citation)}, and evidence for ellipsoidal
variations between transits \dfmtodo{(e.g. citation)}.

In \KT, the precision of these tests is lower and they must be applied with
care.
There are typically only a handful of transits, meaning differences between
``odd'' and ``even'' transits must be large to create a significant
difference.
Searching for ellipsoidal variations is hindered by the short time baseline
and the increased photometric uncertainty in \KT\ data.
Centroid variations are feasible in \KT\ but must be treated differently than
in the original \kepler\ mission where this effect was generally measured
using difference imaging \dfmtodo{(cite)}.

@@

In \papertwo, we will characterize the stars for each of our candidates in
detail but for now it's worth noting that about half \dfmtodo{(IS THIS TRUE?)} of our
planet candidates are orbiting stars selected for \KT\ as M-type stars.
If this rate remains robust after stellar characterization and if these
numbers are representative of the yields in upcoming \KT\ Campaigns, the
\KT\ Mission
will substantially increase the number of planets known to transit cool stars.
